\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-07 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
adding IEEE 14 bus sim results

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.95\linewidth]{IEEE14marginals.png}
\caption{\small{Time evolution of the $(\theta_{i},\omega_{i})$ bivariate marginal PDFs, where $i=1,\hdots,5$, for the Kron-reduced IEEE 14 bus simulation setup described in Sec. \ref{subsec:NumSimIEEEBus}. The $5$ rows above correspond to the $5$ generator nodes--these are buses 1, 2, 3, 6 and 8 in Fig. \ref{fig:Motivating}. The columns correspond to the time snapshots. The colorbar at the bottom shows the marginal PDF values.}}
\vspace*{-0.1in}
\label{fig:IEEE14marginals}
\end{figure*}
